Demanding resources: Converging perceptions of challenge and resource characteristics

### 2023-07-18 SIOP2024/SIOP2024convergence.Rmd
editing output out
output editing

```{r anova}

@@

## 36 former "zeroes" got coded as NA when above scales were changed from rowSums to rowMeans - 7/15/23
analysis$value[analysis$value == "NaN"] <- 0
descr::freq(analysis$value)

@@

repmeas <- ezANOVA(data=analysis, dv=value, wid=person, within=.(scale), type=3, detailed=TRUE)
repmeas
# TukeyHSD(workeraov)  ## Tukeys for temp in paper; biggest contrast p = .099
# psych::describeBy(dataworker$overall, dataworker$JobFamily) (took means from here because `TukeyHSD` only reports relative difference)

>>>>

```{r anova, warning=FALSE, echo=FALSE}

@@

## 36 former "zeroes" got coded as NA when above scales were changed from rowSums to rowMeans - 7/15/23
analysis$value[analysis$value == "NaN"] <- 0
#descr::freq(analysis$value)

@@

repmeas <- ezANOVA(data=analysis, dv=value, wid=person, within=.(scale), type=3, detailed=TRUE)
#repmeas
# TukeyHSD(workeraov)  ## Tukeys for temp in paper; biggest contrast p = .099
# psych::describeBy(dataworker$overall, dataworker$JobFamily) (took means from here because `TukeyHSD` only reports relative difference)

### 2023-07-18 SIOP2024/SIOP2024convergence.tex
editing output out
output editing

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Demanding resources: Converging perceptions of challenge and resource characteristics},
  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\includegraphics{SIOP2024convergence_files/figure-latex/anova-1.pdf}

\begin{verbatim}
## analysis$value 
##                    Frequency   Percent
## 0                        546  13.73239
## 0.0526315789473684         1   0.02515
## 0.0555555555555556         1   0.02515
## 0.0588235294117647         3   0.07545
## 0.0625                     1   0.02515
## 0.0666666666666667         4   0.10060
## 0.0714285714285714         2   0.05030
## 0.0769230769230769         7   0.17606
## 0.0833333333333333        14   0.35211
## 0.0909090909090909        15   0.37726
## 0.1                       21   0.52817
## 0.111111111111111         28   0.70423
## 0.125                     38   0.95573
## 0.133333333333333          4   0.10060
## 0.142857142857143         39   0.98089
## 0.15                       1   0.02515
## 0.153846153846154          4   0.10060
## 0.157894736842105          1   0.02515
## 0.166666666666667         41   1.03119
## 0.176470588235294          2   0.05030
## 0.181818181818182          9   0.22636
## 0.1875                     3   0.07545
## 0.2                       94   2.36419
## 0.214285714285714          3   0.07545
## 0.222222222222222         40   1.00604
## 0.230769230769231          2   0.05030
## 0.25                      84   2.11268
## 0.266666666666667          2   0.05030
## 0.272727272727273         13   0.32696
## 0.277777777777778          1   0.02515
## 0.285714285714286         45   1.13179
## 0.294117647058824          2   0.05030
## 0.3                       38   0.95573
## 0.3125                     5   0.12575
## 0.333333333333333        172   4.32596
## 0.352941176470588          1   0.02515
## 0.357142857142857          3   0.07545
## 0.363636363636364         20   0.50302
## 0.375                     40   1.00604
## 0.384615384615385          5   0.12575
## 0.4                      110   2.76660
## 0.411764705882353          5   0.12575
## 0.416666666666667         15   0.37726
## 0.428571428571429         42   1.05634
## 0.4375                     2   0.05030
## 0.444444444444444         48   1.20724
## 0.45                       1   0.02515
## 0.454545454545455         19   0.47787
## 0.461538461538462          4   0.10060
## 0.466666666666667          2   0.05030
## 0.470588235294118          2   0.05030
## 0.5                      298   7.49497
## 0.529411764705882          3   0.07545
## 0.533333333333333          4   0.10060
## 0.538461538461538          6   0.15091
## 0.545454545454545         24   0.60362
## 0.555555555555556         60   1.50905
## 0.5625                     2   0.05030
## 0.571428571428571         41   1.03119
## 0.583333333333333         14   0.35211
## 0.588235294117647          2   0.05030
## 0.6                      117   2.94266
## 0.611111111111111          2   0.05030
## 0.615384615384615          5   0.12575
## 0.625                     59   1.48390
## 0.631578947368421          1   0.02515
## 0.636363636363636         21   0.52817
## 0.642857142857143          4   0.10060
## 0.647058823529412          5   0.12575
## 0.666666666666667        202   5.08048
## 0.6875                     5   0.12575
## 0.692307692307692          7   0.17606
## 0.7                       46   1.15694
## 0.705882352941177          4   0.10060
## 0.714285714285714         38   0.95573
## 0.727272727272727         29   0.72938
## 0.733333333333333          6   0.15091
## 0.75                     159   3.99899
## 0.769230769230769         10   0.25151
## 0.777777777777778         74   1.86117
## 0.785714285714286          8   0.20121
## 0.8                      125   3.14386
## 0.8125                     1   0.02515
## 0.818181818181818         20   0.50302
## 0.823529411764706          3   0.07545
## 0.833333333333333         59   1.48390
## 0.846153846153846          3   0.07545
## 0.857142857142857         38   0.95573
## 0.866666666666667          7   0.17606
## 0.875                     47   1.18209
## 0.882352941176471          8   0.20121
## 0.888888888888889         48   1.20724
## 0.894736842105263          1   0.02515
## 0.9                       50   1.25755
## 0.909090909090909         16   0.40241
## 0.916666666666667         15   0.37726
## 0.923076923076923          4   0.10060
## 0.928571428571429          9   0.22636
## 0.933333333333333          8   0.20121
## 0.9375                     5   0.12575
## 0.941176470588235          8   0.20121
## 1                        640  16.09658
## Total                   3976 100.00000
\end{verbatim}

\begin{verbatim}
## $ANOVA
##        Effect DFn  DFd        SSn      SSd         F             p p<.05
## 1 (Intercept)   1  567 1146.04761 171.5620 3787.6047 3.580669e-253     *
## 2       scale   6 3402   92.90682 182.9607  287.9206 7.175910e-299     *
##         ges
## 1 0.7637413
## 2 0.2076457
## 
## $`Mauchly's Test for Sphericity`
##   Effect         W            p p<.05
## 2  scale 0.4208255 6.425345e-91     *
## 
## $`Sphericity Corrections`
##   Effect       GGe         p[GG] p[GG]<.05       HFe         p[HF] p[HF]<.05
## 2  scale 0.7801204 6.574489e-234         * 0.7874087 4.617424e-236         *
\end{verbatim}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Demanding resources: Converging perceptions of challenge and resource characteristics},
  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@
